We have two types of actors:
\begin{itemize}
\item User: Visitor.
\item Admin: User with access to the administration panel.
\end{itemize}

\section{Clicking on a radar at the map}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Checks if there is data for the date
\item If images is not generated, it will generate them real time.
\item Radar shows images over an interval.
\item \emph{One click for play/pause and double click for reset.}
\item When there is no more data, the radar resets.
\end{itemize}
\textbf{Alternative scenario:} 
\begin{enumerate}
\item No data is available for that moment and a message appears.
\end{enumerate}

\section{Clicking on a wind farm at the map}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Opens chart dialog.
\item Chart data is retrieved in the background
\item Data is visualized if available
\end{itemize}

\section{Changing view in chart for wind farm}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{enumerate}
\item Changing to 2-week view.
\begin{itemize}
\item Changing chart view interval to 2 weeks.
\item Load new data for the new interval.
\end{itemize}
\item Changing to weekly view.
\begin{itemize}
\item Changing chart view interval to 1 week.
\item Load new data for the new interval.
\end{itemize}
\item Changing to daily view.
\begin{itemize}
\item Changing chart view interval to 1 day.
\item Load new data for the new interval.
\end{itemize}
\end{enumerate}

\section{Changing data set in chart}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Selecting a new data set
\item The data is retrieved from the server
\item Visualize the data if available
\end{itemize}
\textbf{Alternative scenario}
\begin{itemize}
\item Unselecting a data set
\item The data is removed from the chart
\end{itemize}

\section{Using control buttons in chart for wind farm}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{enumerate}
\item Pressing fast backward.
\begin{itemize}
\item Go two weeks back on 2-week view, one week back on weekly view and one day on daily view.
\item Loads new data.
\end{itemize}
\item Pressing backward.
\begin{itemize}
\item Go one week back on 2-week view, one day back on weekly view and one hour on daily view.
\item Loads new data.
\end{itemize}
\item Pressing play.
\begin{itemize}
\item Change to daily view and go one hour forward every second.
\item Loads new data.
\end{itemize}
\item Pressing forward.
\begin{itemize}
\item Go one week forward on 2-week view, one day forward on weekly view and one hour on daily view.
\item Loads new data.
\end{itemize}
\item Pressing fast forward.
\begin{itemize}
\item Go two weeks forward on 2-week view, one week forward on weekly view and one day on daily view.
\item Loads new data.
\end{itemize}
\end{enumerate}

\section{Upload file}
\textbf{Actor:} Admin

\textbf{Scenario:}
\begin{itemize}
\item Sign in with correct username and password.
\item Add new file (CSV, WRK, ZIP) and enter correct timezone.
\item If file is ZIP, it will decompress.
\item File is uploaded.
\item File is being parsed.
\end{itemize}
\textbf{Alternative scenario:} 
\begin{enumerate}
\item Sign in with wrong username or password.
\item Adding file that is not correct format and get an error message.
\item Adding ZIP file, but files inside zip are not correct. They will be skipped.
\item File exists and will not be uploaded.
\end{enumerate}